---
title: "GPS Data Tutorials"
author: "Melissa Tobin"
date: '2018-09-17'
output:
      html_document:
        keep_md: true
Completing tutorials for GPS data to get ready for data analysis
---
## Knit File

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install and load packages

```{r}
library(tidyverse)
library(dplyr)
install.packages("devtools")
library(devtools)
install.packages("stringr")
library(stringr)
install.packages("maps")
library(maps)
install.packages("mapdata")
library(mapdata)
install.packages("ggmap")
library(ggmap)
install.packages("readr")
library(readr)
```

## Reading in data

```{r}
gps_data <- read_csv("coordinates.csv")
cchs <- read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/HKR6130_MUN-master/cchs.csv")
```

# HKR 6130 - Week 8 Tutorial - GPS
## Read in GPS Data

```{r}
gps <- read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/HKR6130_MUN-master/gps_user1.csv")
gps <- gps[order(gps$uuid),]
head(gps)
```

## Add new variable to GPS dataset

```{r}
gps$timestamp2 <- as.Date(as.factor(gps$timestamp))
```

## Unique participant in GPS data

```{r}
users <- unique(gps$uuid)
table(users)
```

## Exploring participant data

```{r}
day_1 <- "2017-07-14"
user <- "DFuller"
user_ij <- filter(gps, gps$timestamp2 == day_1)
```

## Plotting the altitude record

```{r}
ggplot(data = user_ij, aes(x = timestamp, y = altitude)) +
  geom_point()+
  geom_line(aes(group = 1)) +
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) +
  labs(y = "Altitude")
```

## PLot the speed at each GPS Location 

```{r}
ggplot(data = user_ij, aes(x = timestamp, y = speed)) +
  geom_point() +
  geom_line(aes(group = 1)) +
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) +
  labs(y = "speed")
```

## Plot the GPS Points without a map background

```{r}
title = paste("Activity route of participant\n", as.character(user) , "\n", "on day", day_1, sep = " ")
ggplot()+
  geom_point(data = user_ij, aes(x = longitude, y = latitude), size = 1.5, color = "red") +
  labs(title = title, x = "Longitude", y = "Latitude")
```

## Map Tutorial using ggmaps
Reproducible Research Course by Eric C. Anderson for (NOAA/SWFSC)

```{r}
usa <- map_data("usa")
dim(usa)
head(usa)
tail(usa)
```

## Plotting the USA Map

```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group)) + coord_fixed(1.3)
```

## PLotting the USA Map with an outline 

```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group), fill = NA, color = "blue") +
  coord_fixed(1.3)
```

## Plotting the USA Map with a fill and outline

```{r}
ggl <- ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group), fill = "violet", color = "blue") +
  coord_fixed(1.3)
ggl
```

## Adding points to the USA map 

```{r}
labs <- data.frame(
  long = c(-122.064873, -122.306417),
  lat = c(36.951968, 47.644855),
  names = c("SWFSC-FED", "NWFSC"), 
  stringsAsFactors = FALSE
)
ggl +
  geom_point(data = labs, aes(x = long, y = lat), color = "black", size = 5) +
  geom_point(data = labs, aes(x = long, y = lat), color = "yellow", size = 4)
ggl
```

## Group aesthetic function 
group = group function is important because it makes sure to connect all of the group 1's and group 2's but not group 1 with group 2. 
```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat), fill = "violet", color = "blue") +
  geom_point(data = labs, aes(x = long, y = lat), color = "black", size = 5) +
  geom_point(data = labs, aes(x = long, y = lat), color = "yellow", size = 4) +
  coord_fixed(1.3)
```

## State maps

```{r}
states <- map_data("state")
dim(states)
head(states)
tail(states)

```

## Plotting the states
guides(fill = FALSE) - leaves out the color legend
```{r}
ggplot(data = states) +
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white")+
  coord_fixed(1.3)+
  guides(fill = FALSE)
```

## Plotting only certain states using subet

```{r}
west_coast <- subset(states, region %in% c("california", "oregon", "washington"))

ggplot(data = west_coast)+
  geom_polygon(aes(x = long, y = lat, group = group, fill = region),color = "black") +
  coord_fixed(1.3)

```

## Focusing on California Data

```{r}
ca_df <- subset(states, region == "california")
head(ca_df)

counties <- map_data("county")
ca_county <- subset(counties, region == "california")
head(ca_county)
```

## Plotting California Data
unable to get theme_nothing to work - theme_nothing() is supposed to take out the axis gridlines and background
```{r}
ca_base <- ggplot(data = ca_df) +
  geom_polygon(aes(x = long, y = lat, group = group), color = "black", fill = "grey")+
  coord_fixed(1.3) 
ca_base

```

## Plotting county boundries

```{r}
ca_base +
  geom_polygon(data = ca_county, fill = NA, color = "white") +
  geom_polygon(color = "black", fill = NA)
```

```{r}
 x <- readLines("data/ca-counties-wikipedia.txt")
    pop_and_area <- str_match(x, "^([a-zA-Z ]+)County\t.*\t([0-9,]{2,10})\t([0-9,]{2,10}) sq mi$")[, -1] %>%
      na.omit() %>%
      str_replace_all(",", "") %>% 
      str_trim() %>%
      tolower() %>%
      as.data.frame(stringsAsFactors = FALSE)
```

## ggmap
Entering in the data
```{r}
name <- c("a17", "a20-24", "a25-28", "a18-19", "a35-36", "a31", "a38", "a43")
lon <- c(-119.8703, -119.7563, -199.7537, -119.7573, -119.7467, -119.7478, -119.7447, -119.7437)
lat <- c(34.75474, 34.75380, 34.75371, 34.75409, 34.75144, 34.75234, 34.75230, 34.75251)
sisquoc <- data.frame(name = name, lon = lon, lat = lat)
library(ggmap)
```

## using make_bbox function
Bounding box - sets the boundries for our map
```{r}
sbbox <- make_bbox(lon = sisquoc$lon, lat = sisquoc$lat, f = .1) 
```

## Making the map using ggmap
Unable to get the google map to load - it says "sorry we have no imagery here"
```{r}
sq_map <- get_map(location = sbbox, maptype = "satellite", source = "google")

ggmap(sq_map) +geom_point(data = sisquoc, mapping = aes(x = lon, y = lat), color = "red")
```

## Trying a different approach using mean lat and lon with ggmaps

```{r}
means_2 <- sapply(sisquoc[2:3], mean)
sq_map2 <- get_map(location = means_2, maptype = "satellite", source = "google", zoom = 15)
ggmap(sq_map2) +
  geom_point(data = sisquoc, color = "red", size = 4) +
  geom_text(data = sisquoc, aes(label = paste(" ", as.character(name), sep = "")), angle = 60, hjust = 0, color = "yellow")
```

## Bike Ride Data - read the data in

```{r}
read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis/bike-ride.csv")
bike <- read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis/bike-ride.csv")
head(bike)
```

## Mapping the bike data - Terrain Map
```{r}
bikemap1 <- get_map(location = c(-122.080954, 36.971709), maptype = "terrain", source = "google", zoom = 14)
ggmap(bikemap1) +
  geom_path(data = bike, aes(color = elevation), size = 3, lineend = "round") +
  scale_color_gradientn(colours = rainbow(7), breaks = seq(25, 200, by = 25))
```

## Roadmap View
```{r}
bikemap2 <- get_map(location = c(-122.080954, 36.971709), maptype = "roadmap", source = "google", zoom = 14)
ggmap(bikemap2) +
  geom_path(data = bike, aes(color = elevation), size = 3, lineend = "round") +
  scale_color_gradientn(colours = rainbow(7), breaks = seq(25, 200, by = 25))
```

## Satellite View
```{r}
bikemap3 <- get_map(location = c(-122.080954, 36.971709), maptype = "satellite", source = "google", zoom = 14)
ggmap(bikemap3) +
  geom_path(data = bike, aes(color = elevation), size = 3, lineend = "round") +
  scale_color_gradientn(colours = rainbow(7), breaks = seq(25, 200, by = 25))
```

## Hybrid View
```{r}
bikemap4 <- get_map(location = c(-122.080954, 36.971709), maptype = "hybrid", source = "google", zoom = 14)
ggmap(bikemap4) +
  geom_path(data = bike, aes(color = elevation), size = 3, lineend = "round") +
  scale_color_gradientn(colours = rainbow(7), breaks = seq(25, 200, by = 25))
```

## Fish Sampling Locations - reading in new data and looking at the data

```{r}
bc <- readRDS("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/Thesis/bc_sites.rds")

bc %>% select(state_or_province: sub_location, longitude, latitude)

bc %>% group_by(sector, region, area) %>% tally()
```

## Making a map using make_bbox - round 2

```{r}
bc_bbox <- make_bbox(lat = latitude, lon = longitude, data = bc)
bc_bbox
bc_big <- get_map(location = bc_bbox, source = "google", maptype = "terrain")
ggmap(bc_big) +
  geom_point(data = bc, mapping = aes(x = longitude, y = latitude, color = sector))

ggmap(bc_big) +
  geom_point(data = bc, mapping = aes(x = longitude, y = latitude, color = region))
```

```{r}

```

