---
title: "Thesis Analysis"
author: "Melissa Tobin"
date: '2018-09-17'
output:
      html_document:
        keep_md: true
---
## Knit File

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install and load packages

```{r}
library(tidyverse)
library(dplyr)
install.packages("devtools")
library(devtools)
install.packages("stringr")
library(stringr)
install.packages("maps")
library(maps)
install.packages("mapdata")
library(mapdata)
install.packages("ggmap")
library(ggmap)
```

## Reading in data

```{r}
gps_data <- read_csv("coordinates.csv")
cchs <- read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/HKR6130_MUN-master/cchs.csv")
```

# HKR 6130 - Week 8 Tutorial - GPS
## Read in GPS Data

```{r}
gps <- read_csv("/Volumes/hkr-storage/Research/dfuller/Walkabilly/people/Melissa Tobin/HKR6130_MUN-master/gps_user1.csv")
gps <- gps[order(gps$uuid),]
head(gps)
```

## Add new variable to GPS dataset

```{r}
gps$timestamp2 <- as.Date(as.factor(gps$timestamp))
```

## Unique participant in GPS data

```{r}
users <- unique(gps$uuid)
table(users)
```

## Exploring participant data

```{r}
day_1 <- "2017-07-14"
user <- "DFuller"
user_ij <- filter(gps, gps$timestamp2 == day_1)
```

## Plotting the altitude record

```{r}
ggplot(data = user_ij, aes(x = timestamp, y = altitude)) +
  geom_point()+
  geom_line(aes(group = 1)) +
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) +
  labs(y = "Altitude")
```

## PLot the speed at each GPS Location 

```{r}
ggplot(data = user_ij, aes(x = timestamp, y = speed)) +
  geom_point() +
  geom_line(aes(group = 1)) +
  theme(axis.ticks.x = element_blank(), 
        axis.text.x = element_blank()) +
  labs(y = "speed")
```

## Plot the GPS Points without a map background

```{r}
title = paste("Activity route of participant\n", as.character(user) , "\n", "on day", day_1, sep = " ")
ggplot()+
  geom_point(data = user_ij, aes(x = longitude, y = latitude), size = 1.5, color = "red") +
  labs(title = title, x = "Longitude", y = "Latitude")
```

## Map Tutorial using ggmaps
Reproducible Research Course by Eric C. Anderson for (NOAA/SWFSC)

```{r}
usa <- map_data("usa")
dim(usa)
head(usa)
tail(usa)
```

## Plotting the USA Map

```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group)) + coord_fixed(1.3)
```

## PLotting the USA Map with an outline 

```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group), fill = NA, color = "blue") +
  coord_fixed(1.3)
```

## Plotting the USA Map with a fill and outline

```{r}
ggl <- ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat, group = group), fill = "violet", color = "blue") +
  coord_fixed(1.3)
ggl
```

## Adding points to the USA map 

```{r}
labs <- data.frame(
  long = c(-122.064873, -122.306417),
  lat = c(36.951968, 47.644855),
  names = c("SWFSC-FED", "NWFSC"), 
  stringsAsFactors = FALSE
)
ggl +
  geom_point(data = labs, aes(x = long, y = lat), color = "black", size = 5) +
  geom_point(data = labs, aes(x = long, y = lat), color = "yellow", size = 4)
ggl
```

## Group aesthetic function 
group = group function is important because it makes sure to connect all of the group 1's and group 2's but not group 1 with group 2. 
```{r}
ggplot() +
  geom_polygon(data = usa, aes(x = long, y = lat), fill = "violet", color = "blue") +
  geom_point(data = labs, aes(x = long, y = lat), color = "black", size = 5) +
  geom_point(data = labs, aes(x = long, y = lat), color = "yellow", size = 4) +
  coord_fixed(1.3)
```

## State maps

```{r}
states <- map_data("state")
dim(states)
head(states)
tail(states)

```

## Plotting the states
guides(fill = FALSE) - leaves out the color legend
```{r}
ggplot(data = states) +
  geom_polygon(aes(x = long, y = lat, fill = region, group = group), color = "white")+
  coord_fixed(1.3)+
  guides(fill = FALSE)
```

## Plotting only certain states using subet

```{r}
west_coast <- subset(states, region %in% c("california", "oregon", "washington"))

ggplot(data = west_coast)+
  geom_polygon(aes(x = long, y = lat, group = group, fill = region),color = "black") +
  coord_fixed(1.3)

```

## Focusing on California Data

```{r}
ca_df <- subset(states, region == "california")
head(ca_df)

counties <- map_data("county")
ca_county <- subset(counties, region == "california")
head(ca_county)
```

## Plotting California Data

```{r}
ca_base <- ggplot(data = ca_df) +
  geom_polygon(aes(x = long, y = lat, group = group), color = "black", fill = "grey")+
  coord_fixed(1.3) 
ca_base
```

